Generating Simulated Data

### 2021-03-23 docs/SimData.Rmd

We can get surface and bottom temp from atlatis using the layers from each polygon, with layer 0 (?) being the surface and the maximum layer in the polygon being the bottom. 
```{r}

# taken from existing load_nc

file.nc <- file.path(d.name, "outputnordic_runresults_01.nc")

  # Load ATLANTIS output!
  at_out <- RNetCDF::open.nc(con = file.nc)

  # Get info from netcdf file! (Filestructure and all variable names)
  var_names_ncdf <- sapply(seq_len(RNetCDF::file.inq.nc(at_out)$nvars - 1),
    function(x) RNetCDF::var.inq.nc(at_out, x)$name)
  n_timesteps <- RNetCDF::dim.inq.nc(at_out, 0)$length
  n_boxes     <- RNetCDF::dim.inq.nc(at_out, 1)$length
  n_layers    <- RNetCDF::dim.inq.nc(at_out, 2)$length

RNetCDF::close.nc(at_out)

@@

truetempagg <- atlantisom::load_nc_physics(dir = d.name,
                  file_nc = "outputnordic_runresults_01.nc",
                  physic_variables = "Temp",
                  aggregate_layers = TRUE,
                  bboxes = atlantisom::get_boundary(NOBAom_ms$boxpars))

>>>>

We can get surface and bottom temp from Atlantis using the layers from each polygon, with layer 0 being the bottom and the maximum layer in the polygon being the surface (according to the [Atlantis wiki/Atlantis output files/Atlantis NetCDF structure](https://confluence.csiro.au/display/Atlantis/Atlantis+NetCDF+Structure). 
```{r surveytemp, eval=FALSE}

# taken from existing load_nc to explore
# file.nc <- file.path(d.name, "outputnordic_runresults_01.nc")
# 
#   # Load ATLANTIS output!
#   at_out <- RNetCDF::open.nc(con = file.nc)
# 
#   # Get info from netcdf file! (Filestructure and all variable names)
#   var_names_ncdf <- sapply(seq_len(RNetCDF::file.inq.nc(at_out)$nvars - 1),
#     function(x) RNetCDF::var.inq.nc(at_out, x)$name)
#   n_timesteps <- RNetCDF::dim.inq.nc(at_out, 0)$length
#   n_boxes     <- RNetCDF::dim.inq.nc(at_out, 1)$length
#   n_layers    <- RNetCDF::dim.inq.nc(at_out, 2)$length
# 
# RNetCDF::close.nc(at_out)

@@

# this averages all depth layers, don't want this
# truetempagg <- atlantisom::load_nc_physics(dir = d.name,
#                   file_nc = "outputnordic_runresults_01.nc",
#                   physic_variables = "Temp",
#                   aggregate_layers = TRUE,
#                   bboxes = atlantisom::get_boundary(NOBAom_ms$boxpars))

truebottomtemp <- truetemp %>%
  filter(layer == 0) # according to Atlantis wiki, layer 0 is bottom

truesurfacetemp <- truetemp %>%
  filter(layer<7) %>%  #layer 7 is always identical temp to layer 0, may be the added sediment layer?
  group_by(polygon, time) %>%
  filter(layer==max(layer)) %>%
  ungroup

surveyenv <- function(trueenv, 
                      survboxes,
                      survtimes) {
  surveydat <- trueenv %>%
    dplyr::filter(polygon %in% survboxes) %>%
    dplyr::filter(time %in% survtimes)

  return(surveydat)
}

omlist_ss <- NOBAom_ms
source(here("simulated-data/config/omdimensions.R"))

#need to weight by polygon area to get mean annual temp time series for each survey
boxarea <- map_dfr(NOBAom_ms$boxpars$boxes, "area") %>%
  pivot_longer(everything(), names_to = "polygon", values_to = "area") %>%
  mutate(polygon = as.integer(polygon)) %>%
  mutate(proparea = area/sum(area))

source(here("simulated-data/config/mssurvey_fall.R"))

fallcensus_bottomtemp <- surveyenv(truebottomtemp, survboxes = survboxes, survtimes = survtime)

fallcensus_btempindex <- left_join(fallcensus_bottomtemp, boxarea) %>%
  dplyr::group_by(time) %>%
  dplyr::summarise(meantemp = weighted.mean(atoutput, proparea)) %>%
  dplyr::mutate(year = ceiling(time/stepperyr)) %>%
  dplyr::select(year, meantemp) %>%
  write_csv(paste0(o.name,"observation_temperature_NOBA_",survey.name,".csv"))

source(here("simulated-data/config/mssurvey_spring.R"))

springcensus_bottomtemp <- surveyenv(truebottomtemp, survboxes = survboxes, survtimes = survtime)

springcensus_btempindex <- left_join(springcensus_bottomtemp, boxarea) %>%
  dplyr::group_by(time) %>%
  dplyr::summarise(meantemp = weighted.mean(atoutput, proparea)) %>%
  dplyr::mutate(year = ceiling(time/stepperyr)) %>%
  dplyr::select(year, meantemp) %>%
  write_csv(paste0(o.name,"observation_temperature_NOBA_",survey.name,".csv"))

source(here("simulated-data/config/mssurvey_fall_01.R"))

fallnearbox_bottomtemp <- surveyenv(truebottomtemp, survboxes = survboxes, survtimes = survtime)

fallnearbox_btempindex <- left_join(fallnearbox_bottomtemp, boxarea) %>%
  dplyr::group_by(time) %>%
  dplyr::summarise(meantemp = weighted.mean(atoutput, proparea)) %>%
  dplyr::mutate(year = ceiling(time/stepperyr)) %>%
  dplyr::select(year, meantemp) %>%
  write_csv(paste0(o.name,"observation_temperature_NOBA_",survey.name,".csv"))

source(here("simulated-data/config/mssurvey_spring_01.R"))

springnearbox_bottomtemp <- surveyenv(truebottomtemp, survboxes = survboxes, survtimes = survtime)

springnearbox_btempindex <- left_join(springnearbox_bottomtemp, boxarea) %>%
  dplyr::group_by(time) %>%
  dplyr::summarise(meantemp = weighted.mean(atoutput, proparea)) %>%
  dplyr::mutate(year = ceiling(time/stepperyr)) %>%
  dplyr::select(year, meantemp) %>%
  write_csv(paste0(o.name,"observation_temperature_NOBA_",survey.name,".csv"))
